\documentclass{beamer}
\usetheme{Madrid}
%Information to be included in the title page:
\title{Document-based Question Answering}
\author{Hachem Betrouni}
\institute{National Polytechnic school of Algiers, Industrial Engineering Department, Data Science and AI, Algiers, hachem.betrouni@g.enp.edu.dz}
\date{2023}

\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents[currentsection]
  \end{frame}
}

\begin{document}
\frame{
    \centering
    {\small People's Democratic Republic of Algeria}\\
    {\small Ministry of Higher Education and Scientific Research}\\
    {\small National Polytechnic School of Algiers}
    \titlepage
    \begin{tabular}{lrlcc}
        \textbf{President} & Mme. Latifa DEBBI  & Prof. & ENP,  Alger \\
        \textbf{Examiner} & Mr. Salah Eddine TACHI & MCA. & ENP,  Alger \\
        \textbf{Supervisor} & Mr. Hakim FOURAR LAIDI  & MCA. & ENP,  Alger \\
    \end{tabular}
}

\section{Introduction}
\begin{frame}
    \frametitle{Introduction}
    In today's market, creating value goes beyond providing standard solutions. 
    The AI consulting industry has advanced with the introduction of Large Language Models (LLMs) and other fundamental models. 
    To create value, bespoke AI solutions are now required, 
    tailored to specific needs and surpassing basic predictions and recommendations.
\end{frame}

\begin{frame}
    \begin{block}{The requirements}
        The requirements are no longer to predict a number, but to explain the prediction, it's no longer to recommend a blog title but to generate its whole content.
    \end{block}

    \begin{alertblock}{Market shift}
        Today we are well aware that answering organizations' needs for innovation has shifted from writing consulting reports 
        to building tangible assets that concretize the added value. Today, clients are expecting specialized solutions to their problems, 
        rather than the boilerplate solutions consultants traditionally provided.
    \end{alertblock}
\end{frame}

\section{BIGmama technology}
\begin{frame}
    \frametitle{BIGmama technology}
    BIGmama is a French registered startup with an Algerian extension, specialized in data science and AI. 
    They have been developing bespoke predictive applications for more than 8 years.
\end{frame}

\begin{frame}
    \begin{block}{Mission}
        BIGmama's mission is to democratize the access to bespoke AI applications, 
        From an original method based on the know-how developed while working with their partners for nearly a decade, 
        they are able of identifying and extracting expertise as well as combine it with machine learning system (Hybrid AI).
    \end{block}

    \begin{block}{Vision}
        Data science will soon become a commodity, the arrival of large language models (which are considered foundational models in NLP) 
        mark but a start of a new wave of foundational models. 
        In the near future, we can expect the emergence of generalist models that are equivalent to ChatGPT but specialized in computer vision tasks, 
        forecasting, pattern recognition, and other domains.
    \end{block}
\end{frame}

\end{document}